Hamiltonian Mechanics unter besonderer Ber\"ucksichtigung der h\"ohreren Lehranstalten

### 2017-01-16 assump.tex
modif 01/16/2017

  \begin{definition}{(Ring-LWE)}
    Let $R = \mathbb{Z}[x] /\langle x^n +1\rangle$, $R_q = R/ qR$ and $\chi$ be a distribution over $R$.
    The decisional ring learning with errors assumption (denoted by $RLWE_{q, \chi}$) states that:
    \begin{align*}
      \{ (a_i, a_i \cdot s + e_i)\} &\approx_c \{(a_i, u_i)\},
    \end{align*}
    for any polynomial number of samples, where $a_i \sample R_q$, $e_i \sample \chi$, $u_i \sample R_q$ and $s \sample R_q$.
  \end{definition}

>>>>

  \begin{definition}{(Ring-LWE)}
    The $\vec{f}$-LWE problem can be defined as follows.
    Let $R = \mathbb{Z}[x] /\langle \vec{f}\rangle$, $R_q = R/ qR$ and $\chi$ be a distribution over $R$.
    The decisional ring learning with errors assumption (denoted by $\vec{f}-RLWE_{q, \chi}$) states that:
    \begin{align*}
      \{ (a_i, a_i \cdot s + e_i)\} &\approx_c \{(a_i, u_i)\},
    \end{align*}
    for any polynomial number of samples, where $a_i \sample R_q$, $e_i \sample \chi$, $u_i \sample R_q$ and $s \sample R_q$.
  \end{definition}

  \begin{definition}{(Ring-SIS)}
    The $\vec{f}$-SIS problem can be defined as follows.
    Let $R = \mathbb{Z}[x] /\langle \vec{f}\rangle$ and $R_q = R/ qR$.
    The ring small integer solution problem (denoted by $\vec{f}-RSIS_{k, q, \beta}$) states that find a solution $(\vec{z}_1, \dots, \vec{z}_k) \in R_q$ and $||\vec{z}_i|| \leq \beta$ of the following problem is hard:
    \begin{align*}
      \sum_{i= 1}^k \vec{a}_i \vec{z}_i &= \vec{0}~mod~\vec{f}
    \end{align*}
    for any polynomial number of samples, where $\vec{a}_i \sample R_q$
  \end{definition}
